We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-04-20 paper/paper.tex
new plots in the appendix

\section{Results from ELVIS and Illustris1}
\label{appendix:plots}
\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_elvis_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_elvis_ba_ratio.pdf}
\caption{ELVIs results for the quantities presented for the Illustris1-Dark
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_M31_n_11.pdf}
\includegraphics[width=0.48\textwidth]{gaussian_model_elvis_MW_n_11.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
computed from the ELVIS data.
\label{fig:correlations_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_ranked_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_width.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ranked_ba_ratio.pdf}
\caption{Same layout as Figure \ref{fig:scatter_elvis}, this time
  computed from the Illustris-1 data.
\label{fig:scatter_illustris}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{gaussian_model_illustris1_M31_n_11.pdf}
\includegraphics[width=0.48\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
\caption{
Same layout as Figure \ref{fig:correlations_illustrisdm}, this time
computed from the Illustris-1 data.
\label{fig:correlations_illustris}}
\end{figure*}

>>>>

\section{Results from ELVIS and Illustris1}
\label{appendix:plots}
\begin{figure*}
\centering
\includegraphics[width=0.40\textwidth]{input_illustris1_obs_M31_n_11.pdf}
\includegraphics[width=0.40\textwidth]{input_illustris1_obs_MW_n_11.pdf}
\includegraphics[width=0.40\textwidth]{input_illustris1_obs_M31_n_11_normed.pdf}
\includegraphics[width=0.40\textwidth]{input_illustris1_obs_MW_n_11_normed.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_M31_n_11.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_MW_n_11.pdf}
\caption{ELVIs results for the quantities presented for the Illustris1-Dark
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.40\textwidth]{input_elvis_obs_M31_n_11.pdf}
\includegraphics[width=0.40\textwidth]{input_elvis_obs_MW_n_11.pdf}
\includegraphics[width=0.40\textwidth]{input_elvis_obs_M31_n_11_normed.pdf}
\includegraphics[width=0.40\textwidth]{input_elvis_obs_MW_n_11_normed.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_M31_n_11.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_MW_n_11.pdf}
\caption{ELVIs results for the quantities presented for the Illustris1-Dark
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1dark_M31_n_12.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1dark_MW_n_12.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_M31_n_12.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_illustris1_MW_n_12.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_M31_n_12.pdf}
\includegraphics[width=0.40\textwidth]{gaussian_model_elvis_MW_n_12.pdf}
\caption{ELVIs results for the quantities presented for the Illustris1-Dark
  simulation in Figures  \ref{fig:scatter_width},
  \ref{fig:scatter_ca_ratio}, \ref{fig:scatter_ba_ratio}.
Upper row corresponds to the raw values from observations and
simulated pairs, while the second row normalizes the same values to
the mean and standard deviation on its spherically randomized
counterparts. 
\label{fig:scatter_elvis}}
\end{figure*}
